{Automatic Least-Effort Contextual Learning}

### 2017-03-09 etc/paper.tex
added citations for flashfill

The augmented EC algorithm will be tested in the domain of string
transformation, chosen because it has potential for common underlying
structure between tasks. This section is very much {\bf TODO} (needs
results).

@@

    In \emph{Advances in Neural Information Processing Systems} (pp.
    2672-2680).

@@

>>>>

The augmented EC algorithm will be tested in the domain of string
transformation \cite{gulwani11}\cite{dechter14}, chosen because it has
potential for common underlying structure between complex tasks. Microsoft
Excel's FlashFill implements program induction for string transformations,
but has not been demonstrated to utilize composition over previously learned
programs. This section is very much {\bf TODO} (needs figures, results, etc).

@@

    In \emph{Advances in Neural Information Processing Systems} (pp.  2672-2680).

@@

  \bibitem{gulwani11}
    Gulwani, S. (2011).
    Automating string processing in spreadsheets using input-output examples.
    In \emph{ACM SIGPLAN Notices} (Vol. 46, No. 1, pp. 317-330). ACM.
  \bibitem{dechter14}
    Lin, D., Dechter, E., Ellis, K., Tenenbaum, J., \& Muggleton, S. (2014).
    Bias reformulation for one-shot function induction.
    In \emph{Proceedings of the Twenty-first European Conference on Artificial Intelligence} (pp. 525-530). IOS Press.
